---
title: "purrr map & map2 functions"
author: "FRK"
date: "7/29/2021"
output: 
  html_document:
    highligh: tango
    theme: united
    toc: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
    number_sections: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Data

```{r}
require(tidyverse)

d <- tibble(group = c("HRT", "Placebo"),
            MeanHDL  = c(8.1, 2.4),
            sdHDL = c(10.5, 4.3))
d

```

# **map** function, 5 ways

## With Just function name

```{r}
d %>%
  mutate(logldl = map(MeanHDL, log)) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(logldl))
```

## With mentioning additional parameters

```{r}
d %>%
  mutate(logldl = map(MeanHDL, log, base = 2)) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(logldl))
```


## With a ~ sign, bracket and .x

```{r}
d %>%
  mutate(logldl = map(MeanHDL, ~log(.x))) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(logldl))
```

## With ~, bracket and addictional parameter

```{r}
d %>%
  mutate(logldl = map(MeanHDL, ~log(.x, base = 2))) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(logldl))
```

## With **..1** to mention the first variable as first argument

```{r}

d %>%
  mutate(logldl = map(MeanHDL, ~log(..1))) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(logldl))
```

# **map2** function, 4 ways


## With Just function name

```{r}
d %>%
  mutate(simldl = map2(MeanHDL, sdHDL, rnorm, n = 1000)) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(simldl))
```

## With a ~ sign, bracket and .x , .y

```{r}

d %>%
  mutate(simldl = map2(MeanHDL, sdHDL, ~rnorm(1000, .x, .y))) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(simldl))
```

## With **..1** to mention the first variable as first argument, and second variable as second argument

```{r}
d %>%
  mutate(simldl = map2(MeanHDL, sdHDL, ~rnorm(1000, ..1, ..2))) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(simldl))
```

## Rotating the arguments list will result in different result

```{r}
d %>%
  mutate(simldl = map2(MeanHDL, sdHDL, ~rnorm(1000, ..2, ..1))) %>% 
  unnest() %>% 
  group_by(group) %>% 
  summarise(mean(simldl))

```

